Paper 1: Instrument development

### 2024-09-04 Rmd/Paper1.Rmd
Changed filename of dataset to correspond with paper2

```{r}
# make tibble into data.frame to treat it similarly to pilot dataset
data_TRELIS_Q <- data.frame(data_TRELIS_Q)
```

@@

```{r save_data_TRELIS_Q}
save(data_TRELIS_Q, 
     file="../data/processed_data/tpack-trelis_q_paper1_2023.Rdata")
```

@@

```{r}
# load data
load(file="../data/processed_data/tpack-pilot_2022.Rdata") 
load(file="../data/processed_data/tpack-trelis_q_paper1_2023.Rdata")
```

>>>>

```{r}
# readxls stores as tibble, not dataframe?
# make tibble into data.frame to treat it similarly to pilot dataset
data_TRELIS_Q <- data.frame(data_TRELIS_Q)
```

@@

```{r save_data_TRELIS_Q}
save(data_TRELIS_Q, 
     file="../data/processed_data/tpack-trelis_q_partial_2023-paper1.Rdata")
```

@@

```{r}
# load data
load(file="../data/processed_data/tpack-pilot_2022.Rdata") 
load(file="../data/processed_data/tpack-trelis_q_partial_2023-paper1.Rdata")
```
